Predicting Sales Level for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-21 paper.tex
Introduction revised
Following JJ's suggestions.
Please @JJ, @pacastillo @7ossam81 check it. ;D

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%First you have to explain why it is enough to predict the level of
%sales, and not the precise number. 
% Antonio - it is true, but how can we justify this, JJ?
% I guess that precision is relative in this kind of methods, since the publisher is not going to print exactly '237' books due to it is the output of a regression method. Instead, there could be a range of books to be printed (as a standard) related with an expected 'low', 'medium', 'high' or 'very high' amount of sales.
% Moreover, I guess that the classification output, considering four classes would work better (more precisely and close to reality) than regression.
% What do you think?
An important task when publishing a new book is determining the number 
of copies to be printed, since doing both a (dramatic) under- or overestimation will lead to important financial losses.
In this paper, we transform this problem into a classification one, defining different sales levels i.e. classes. 
The obtained results will be easier to interpret by publishers than other black-box techniques, 
so these methods can be used as reliable decision-aid tools for publishers, to be considered in their decision as a part of the final stages of the editorial process.

The problem of predicting these levels has been addressed applying cost-sensitive ensemble methods.
% Antonio - explain briefly what are them  and  the followed methodology.
In order to do so, a real dataset collected by a Spanish publishing company, including the complete sales data for books published in Spain across several years, has been used to design and evaluate the prediction models.
% Explain also the method you are using and why it's an improvement over the previous one - JJ
Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.

@@

Specifically, focusing in the publishing process of a new book, deciding the optimal {\em  print run}, i.e. the number of copies to be printed and delivered to bookstores, is a very challenging problem. Thus, it is extremely
important to develop accurate predictive models which could forecast
the future sales a new book will achieve, in order to optimise
production schedules \cite{Fildes2010,Saeed2008,Zhao2001}, to improve the publishing company profits and to minimise losses, due both to the excess or to the scarcity of units. 
%I would eliminate this paragraph. We have it on the other one.
%Since, according to the results reported in \cite{Fildes2010,Saeed2008}, reducing the error in estimated sales leads to an enhancement of the whole production process.
% Antonio - I agree. Removed

@@

Thus, having in mind `the human factor' of the print-run decision process, in this paper we have addressed the problem from a new perspective. We have defined, with the help of an expert, different \textit{levels or ranges of sales}, composing different incremental categories: \textit{Low, Medium, High} and \textit{Very High}. Then, these have been considered as classes, so the given dataset has been labelled according to them, and the problem has been faced as a classification one.

Moreover, handling the problem as a classification task let us to emphasize on the ranges which could be more `critical', e.g. the most profitable books (High and Very High categories). Thus, we can penalize more the misclassification of these categories and, consequently, this tool will perform a better identification of successful books than our previous approach \cite{Castillo2016books}.
% which will be definitely very interesting for publishers.

In order to solve this problem, in this work we propose configuring complex models based on ensembles \cite{Qiu2014} in order to determine the actual level of sales a new book will achieve.
% Antonio - justify why ensembles have been chosen instead of other classification approaches: accuracy, perform, easier to interpret, faster, ...
Another advantage of the proposed approach is that they are easier to interpret than `black box' forecasting methods, such as regression techniques. So, using these ensemble methods, publishers will be able to combine their expert knowledge about the 
market with the obtained models in order to get a reliable estimation 
on book sales level. Moreover, as the output will be just a class, they will be able to understand and justify better their decision.

@@

In this line, the most used techniques to tackle sales forecasting problems have been time-series prediction
\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. %,KayacanUK10}. % Antonio - the last reference doesn't exist
However these methods are strongly dependent on problem data, so the obtained predictions are highly affected by their correctness.
Moreover, this kind of methods are based on using historical data to make time series. However, in the case of new products sales prediction (such as the issue of new books), there is no available historical sales data \cite{ChingChin2010}, 
and only pre-sales data are available \cite{FaderHardie2005,Madsen2008}, 
i.e. variables known before the product is on sale. 
% Antonio - We should rewrite this, since a similar sentence was a weak asseveration in previous paper. The proposed methodology also uses historical data to infer the print-run of new books, so, why is this a problem for Time Series and it is useful for the proposed methods? :/

@@

However, in this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods, defining with the help of an expert different \textit{levels or ranges of sales} in order to compose different incremental categories or classes.

@@

\begin{itemize}
\item Data preparation:

\item Select best base classifier:

\item Select best ensemble classifier:

\item Perform cost-sensitive analysis with best ensemble classifiers:

\item Evaluation and comparison:

@@

In the next stage of the experiments, the ensemble classifiers (i.e. RF, Bagging and AdaBoost) are applied and evaluated. For Bagging and AdaBoost, the base classifier is selected to be the J48 decision tree algorithm. This selection is for three reasons: first, the J48 algorithm achieved very competitive evaluation results in the previous phase. Second, J48 is much faster as a learning algorithm compared to the MLP network which was the second candidate. Third, tree induction algorithms are good candidates as base classifiers in bagging and boosting because support diversity among the learners. It is well known that tree induction algorithms are relatively unstable (i.e. weak) base learners, meaning that small changes in the training data lead to big changes in the developed models. Besides the selection of the base classifier, the effect of the number of iterations is experimented in RF, Bagging and AdaBoost as shown in Figures \ref{fig:PerformanceRF}, \ref{fig:PerformanceBagging} and \ref{fig:PerformanceAdaboost}, respectively. Highest prediction rates are obtained at 60 iterations. The best obtained results for these ensemble classifiers are shown in Table \ref{table:ensemble_classifiers}. It can be seen that all ensemble classifiers achieved higher accuracy rates compared to J48 from the previous stage, achieving around 74\% with approximately 4\% improvement. Inspecting the obtained results for VH class, we can notice that although the recall of the VH hasn't improved much compared to J48, the precision has remarkably increased from 74\% to 81.6\%, 80.8\% and 79.3\% for RF, Adaboost and Bagging, respectively. For the H class, there was an improvement for both measurements, recall and precision. RF and Adaboost achieved approximately 68\% and 67\% for recall and precision, while Bagging achieved 67\% and 66\%, respectively. Also, it can be noticed that there is an improvement in general for the other classes, M and L.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%First you have to explain why it is enough to predict the level of
%sales, and not the precise number. 
% Antonio - it is true, but how can we justify this, JJ?
% I guess that precision is relative in this kind of methods, since the publisher is not going to print exactly '237' books due to it is the output of a regression method. Instead, there could be a range of books to be printed (as a standard) related with an expected 'low', 'medium', 'high' or 'very high' amount of sales.
% Moreover, I guess that the classification output, considering four classes would work better (more precisely and close to reality) than regression.
% What do you think?
An important task when publishing a new book is determining the number 
of copies to be printed, since doing both a (dramatic) under- or overestimation will lead to important financial losses.
In this paper, we transform this problem into a classification one, defining different sales levels. Then, we address the problem of predicting these levels  applying cost-sensitive ensemble methods.
% Antonio - explain briefly what are them
These can be used as reliable decision-aid tools for publishers, as a part of the final stages of the editorial process. 
Thus, a real dataset including the complete sales data for books published in Spain across several years has been used to compute the prediction models.
% Antonio - extend a bit this with the followed methodology.
% Explain also the method you are using and why it's an improvement
% over the previous one - JJ
We evaluate our approach on the real data collected by a Spanish publishing company.
Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.

@@

Specifically, focusing in the publishing process of a new book, deciding the optimal {\em  print run}, i.e. the number of copies to be printed and delivered to bookstores, is a very challenging problem. Thus, it is extremely
important to develop accurate predictive models which could forecast
the future sales a new book will achieve, in order to optimise
production schedules \cite{Fildes2010,Saeed2008,Zhao2001}: to improve the publishing company profits and to minimise losses, due both to the excess or to the scarcity of units. 
%I would eliminate this paragraph. We have it on the other one.
%Since, according to the results reported in \cite{Fildes2010,Saeed2008}, reducing the error in estimated sales leads to an enhancement of the whole production process.
% Antonio - I agree. Removed

@@

Thus, having in mind `the human factor' of the print-run decision process, in this paper we have addressed the problem from another perspective. We have defined, with the help of an expert, different \textit{levels or ranges of sales}, composing different incremental categories: low, medium, high and very high. Then, these have been considered as classes, so the given dataset has been labelled according to them, and the problem has been faced as a classification one.

In order to solve it, in this work we propose configuring complex models based on ensembles \cite{Qiu2014} in order to determine the actual level of sales a new book will achieve.
% Antonio - justify why ensembles have been chosen instead of other classification approaches: accuracy, perform, easier to interpret, faster, ...
Another advantage is they are easier to interpret than `black box' forecasting methods, such as regression techniques. So, using these ensemble methods, publishers will be able to combine their expert knowledge about the 
market with the obtained models in order to get a reliable estimation 
on book sales level. Moreover, as the output will be just a class, they will be able to understand and justify better their decision.

@@

In this line, the most used techniques to tackle sales forecasting problems have been time-series prediction
\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990,KayacanUK10}.
% Antonio - the last reference doesn't exist
However these methods are strongly dependent on problem data, so the obtained predictions are highly affected by their correctness.
Moreover, this kind of methods are based on using historical data to make time series. However, in the case of new products sales prediction (such as the issue of new books), there is no available historical sales data \cite{ChingChin2010}, 
and only pre-sales data are available \cite{FaderHardie2005,Madsen2008}, 
i.e. variables known before the product is on sale. 
% Antonio - We should rewrite this, since a similar sentence was a weak asseveration in previous paper. The proposed methodology also uses historical data to infer the print-run of new books, so, why is this a problem for Time Series and it is useful for the proposed methods? :/

@@

However, in this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods.
% TODO: complete this paragraph.
% Antonio - say why we continue the previous work (what wer the flaws), how are we continuing it, wat we expect to improve, the objective contribution, etc

@@

@@

In the next stage of the experiments, the ensemble classifiers (i.e. RF, Bagging and AdaBoost) are applied and evaluated. For Bagging and AdaBoost, the base classifier is selected to be the J48 decision tree algorithm. This selection is for three reasons: first, the J48 algorithm achieved very competitive evaluation results in the previous phase. Second, J48 is much faster as a learning algorithm compared to the MLP network which was the second candidate. Third, tree induction algorithms are good candidates as base classifiers in bagging and boosting because support diversity among the learners. It is well known that tree induction algorithms are relatively unstable (i.e. weak) base learners, meaning that small changes in the training data lead to big changes in the developed models.
